---
title: "graphs"
author: "Ryan Zhang"
date: "3/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(tidymodels)
library(rstanarm)
library(Hmisc)
library(corrplot)
library(dplyr)
library(data.table) 
library(ggradar)
library(scales)
library(ggplot2)
```

## China Household Corporate Debt Chart

```{r}
mydata <- read_csv(file = "graphs/china_debt.csv",
                   col_types = cols(
                     type = col_character(),
                     proportion = col_double()))

ggplot(mydata, aes(x = "", y = proportion, fill = type)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  scale_fill_discrete(name = "",
                      labels = c("Corporate", "Household")) +
  theme_void() + 
  labs(
    title = "Snapshot of China's Debt",
    subtitle = "June 2018",
    caption = "Source: PBOC") +
  ggsave(filename = "graphs/china_debt.jpg")
```

## China Household Debt Breakdown Chart

```{r}
mydata <- read_csv(file = "graphs/household_debt.csv",
                   col_types = cols(
                     type = col_character(),
                     proportion = col_double()))

ggplot(mydata, aes(x = "", y = proportion, fill = type)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  scale_fill_discrete(name = "",
                      labels = c("Auto Loans", "Credit Cards", "Mortgage",
                                "Operational", "Other Household Consumption")) +
  theme_void() + 
  labs(
    title = "Composition of Household Debt in China",
    subtitle = "June 2018",
    caption = "Source: PBOC\n\nNote: Operational retail loans appear tobe largely lending to the\nself-employed and family businesses, although it is difficult\nto distinguish this type of lending from debt for consumption purposes.") +
  ggsave(filename = "graphs/household_debt.jpg")
```

## China Consumer Credit Chart

```{r}
mydata <- read_csv(file = "graphs/china_consumer_credit.csv",
                   col_types = cols(
                     year = col_double(),
                     consumer_credit = col_double()))

ggplot(mydata, aes(x = year, y = consumer_credit)) +
  geom_line() + 
  theme_bw() + 
  labs(
    title = "China's Consumer Credit Balances",
    subtitle = "2000-2015",
    x = "Year",
    y = "Consumer Credit (Trillions of RMB)",
    caption = "Source: National Bureau of Statistics of China") +
  ggsave(filename = "graphs/china_consumer_credit.jpg")
```

## China US Household Debt Chart

```{r}
mydata <- read_csv(file = "graphs/china_us_household_debt.csv",
                   col_types = cols(
                     date = col_date(format="%m/%d/%y"),
                     china_debt_to_income = col_double(),
                     china_debt_to_gdp = col_double(),
                     us_debt_to_gdp = col_double(),
                     us_debt_to_income = col_double()))

mydata <- mydata %>%
  pivot_longer(names_to = "ratio", 
               values_to = "percent", 
               cols = -date)

ggplot(mydata, aes(x = date, y = percent, color = ratio)) +
  geom_line() + 
  scale_color_discrete(name = "",
                      labels = c("China HH Debt/GDP",
                                 "China HH Debt/HH Income",
                                 "U.S. HH Debt/GDP",
                                 "U.S. HH Debt/HH Income")) +
  ylim(0, 150) + 
  theme_bw() + 
  labs(
    title = "Household (HH) Debt Levels",
    subtitle = "2007-2020",
    x = "Date",
    y = "Percent (%)",
    caption = "Source: PBOC, U.S. Federal Reserve") +
  ggsave(filename = "graphs/china_us_household_debt.jpg")
```

## International BLI Chart

```{r}
mydata <- read_csv(file = "graphs/international_bankruptcy_systems_v3.csv",
                   col_types = cols(
                     jurisdiction = col_character(),
                     bli = col_double())) %>%
  filter((jurisdiction != "Average"))

ggplot(mydata, aes(x = reorder(jurisdiction, bli), y = bli, fill = continent)) +
  geom_bar(stat = "identity") +
  geom_text(size = 4, aes(label = sprintf("%0.2f", bli), hjust = 0.5, vjust = 3)) + 
  scale_fill_manual(values = c("#F8766D", "#00B0F6", "#00BA38")) +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "BLI Scores Around the World",
    x = "Jurisdiction",
    y = "BLI Score",
    fill = "Continent") +
  ggsave(filename = "graphs/international_bankruptcy_systems.jpg")

t.test(mydata$bli[(mydata$continent == "Asia" | mydata$continent == "Shenzhen")], mydata$bli[mydata$continent == "Outside Asia"])
```

## Correlation Matrix (BLI and Macroeconomic Indicators)

```{r}
mydata <- read_csv(file = "graphs/international_bankruptcy_systems_v3.csv",
                   col_types = cols(jurisdiction = col_character())) %>%
  select(-jurisdiction) %>%
  select(-bli_category) %>%
  select(-continent)

res <- cor(mydata)
corrplot(res)

mydata.rcorr = rcorr(as.matrix(mydata))
mydata.coeff = mydata.rcorr$r
round(mydata.coeff, 2)
mydata.p = mydata.rcorr$P
round(mydata.p, 2)

write.csv(mydata.coeff, "graphs/coefficient_matrix_coeff.csv")
write.csv(mydata.p, "graphs/coefficient_matrix_p.csv")
```

## Correlation Plots (BLI and Macroeconomic Indicators)

```{r}
mydata <- read_csv(file = "graphs/international_bankruptcy_systems_v3.csv",
                   col_types = cols(jurisdiction = col_character())) 

ggplot(mydata, aes(x = bli, y = gdp_growth)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and GDP Growth",
    x = "BLI Score",
    y = "Average Percent GDP Growth (2004-2019)") +
  ggsave(filename = "graphs/corr_bli_gdpgrowth.jpg")

ggplot(mydata, aes(x = bli, y = gfcf_growth)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and GFCF Growth",
    x = "BLI Score",
    y = "Average Percent GFCF Growth (2004-2019)") +
  ggsave(filename = "graphs/corr_bli_gfcfgrowth.jpg")

ggplot(mydata, aes(x = bli, y = gii)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and GII Scores",
    x = "BLI Score",
    y = "GII Score") +
  ggsave(filename = "graphs/corr_bli_gii.jpg")

ggplot(mydata, aes(x = bli, y = recovery_rate)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and Creditor Recovery Rates",
    x = "BLI Score",
    y = "Creditor Recovery Rate (Cents on the Dollar)") +
  ggsave(filename = "graphs/corr_bli_recoveryrate.jpg")

ggplot(mydata, aes(x = bli, y = time)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and Time",
    x = "BLI Score",
    y = "Time (Years)") +
  ggsave(filename = "graphs/corr_bli_time.jpg")

ggplot(mydata, aes(x = bli, y = cost)) +
  geom_point() +
  geom_smooth(method = lm, se = TRUE) +
  theme_bw() + 
  labs(
    title = "BLI and Cost",
    x = "BLI Score",
    y = "Cost (Percentage of Debtor's Estate)") +
  ggsave(filename = "graphs/corr_bli_cost.jpg")
```

## Macroeconomic Indicator Radar Plots

```{r}
mydata <- read_csv(file = "graphs/international_bankruptcy_systems_v3.csv",
                   col_types = cols(jurisdiction = col_character()))  %>%
  select(-bli_category) %>%
  select(-continent) %>%
  select(-wb_resolving_insolvency)

colnames(mydata)[1] <- "group"
colnames(mydata)[2] <- "BLI"
colnames(mydata)[3] <- "GDP Growth"
colnames(mydata)[4] <- "GFCF Growth"
colnames(mydata)[5] <- "GII"
colnames(mydata)[6] <- "Recovery Rate"
colnames(mydata)[7] <- "Time"
colnames(mydata)[8] <- "Cost"

mydata <- mydata %>%
  mutate_each(funs(rescale), -group)

mydata_country <- mydata %>%
  filter((group == "Australia" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Australia") +
  ggsave(filename = "graphs/macro_australia.jpg")

mydata_country <- mydata %>%
  filter((group == "Austria" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Austria") +
  ggsave(filename = "graphs/macro_austria.jpg")

mydata_country <- mydata %>%
  filter((group == "Belgium" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Belgium") +
  ggsave(filename = "graphs/macro_belgium.jpg")

mydata_country <- mydata %>%
  filter((group == "Canada" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Canada") +
  ggsave(filename = "graphs/macro_canada.jpg")

mydata_country <- mydata %>%
  filter((group == "Finland" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Finland") +
  ggsave(filename = "graphs/macro_finland.jpg")

mydata_country <- mydata %>%
  filter((group == "Germany" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Germany") +
  ggsave(filename = "graphs/macro_germany.jpg")

mydata_country <- mydata %>%
  filter((group == "Hong Kong" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Hong Kong") +
  ggsave(filename = "graphs/macro_hongkong.jpg")

mydata_country <- mydata %>%
  filter((group == "Israel" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Israel") +
  ggsave(filename = "graphs/macro_israel.jpg")

mydata_country <- mydata %>%
  filter((group == "Japan" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Japan") +
  ggsave(filename = "graphs/macro_japan.jpg")

mydata_country <- mydata %>%
  filter((group == "Malaysia" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Malaysia") +
  ggsave(filename = "graphs/macro_malaysia.jpg")

mydata_country <- mydata %>%
  filter((group == "Shenzhen" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Shenzhen") +
  ggsave(filename = "graphs/macro_shenzhen.jpg")

mydata_country <- mydata %>%
  filter((group == "Shenzhen"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Shenzhen") +
  ggsave(filename = "graphs/macro_shenzhen_only.jpg")

mydata_country <- mydata %>%
  filter((group == "Singapore" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "Singapore") +
  ggsave(filename = "graphs/macro_singapore.jpg")

mydata_country <- mydata %>%
  filter((group == "United Kingdom" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4) +
  theme(legend.position = "none") +
  labs(title = "United Kingdom") +
  ggsave(filename = "graphs/macro_unitedkingdom.jpg")

mydata_country <- mydata %>%
  filter((group == "United States" | group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, base.size = 10) +
  theme(legend.position = "none") +
  labs(title = "United States") +
  ggsave(filename = "graphs/macro_unitedstates.jpg")
```

## BLI Criteria Radar Plots

```{r}
mydata <- read_csv(file = "graphs/bli_scores_v2.csv",
                   col_types = cols(Jurisdiction = col_character()))  %>%
  select(-c(P1, P2, P3, E1, E2, E3, R1, R2, R3, D1, D2, D3, BLI))

colnames(mydata)[1] <- "group"
colnames(mydata)[2] <- "P1"
colnames(mydata)[3] <- "P2"
colnames(mydata)[4] <- "P3"
colnames(mydata)[5] <- "E1"
colnames(mydata)[6] <- "E2"
colnames(mydata)[7] <- "E3"
colnames(mydata)[8] <- "R1"
colnames(mydata)[9] <- "R2"
colnames(mydata)[10] <- "R3"
colnames(mydata)[11] <- "D1"
colnames(mydata)[12] <- "D2"
colnames(mydata)[13] <- "D3"

# Shenzhen

mydata_country <- mydata %>%
  filter(group == "Shenzhen") %>%
  select(-R3)
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), plot.title = "Shenzhen's Scores (by Criterion)") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_shenzhen_by_criterion.jpg")

mydata_country <- mydata %>%
  filter(group == "Shenzhen") %>%
  select(-R3) %>%
  mutate(P = rowMeans(.[,c("P1", "P2", "P3")])) %>%
  mutate(E = rowMeans(.[,c("E1", "E2", "E3")])) %>%
  mutate(R = rowMeans(.[,c("R1", "R2")])) %>%
  mutate(D = rowMeans(.[,c("D1", "D2", "D3")])) %>%
  select(group, P, E, R, D)
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), plot.title = "Shenzhen's Scores (by Category)") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_shenzhen_by_category.jpg")

# All

mydata_country <- mydata %>%
  filter(group == "Average")
  ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), plot.title = "Average Scores (by Criterion)") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_all_by_criterion.jpg")

mydata_country <- mydata %>%
  filter(group != "Average") %>%
  summarise(group = 'Average', 
            P = mean(c(P1, P2, P3)),
            E = mean(c(E1, E2, E3)),
            R = mean(c(R1, R2, R3), na.rm=TRUE),
            D = mean(c(D1, D2, D3)))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), plot.title = "Average Scores (by Category)") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_all_by_category.jpg")

# Shenzhen and All 

mydata_country <- mydata %>%
  filter((group == "Shenzhen") | (group == "Average")) %>%
  select(-R3) %>%
  mutate(P = rowMeans(.[,2:4])) %>%
  mutate(E = rowMeans(.[,5:7])) %>%
  mutate(R = rowMeans(.[,8:9])) %>%
  mutate(D = rowMeans(.[,10:12])) %>%
  select(c(group, P, E, R, D))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), 
         plot.title = "By Criterion") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_shenzhen_all_by_criterion.jpg")

mydata_country <- mydata %>%
  filter((group == "Shenzhen") | (group == "Average")) %>%
  select(-R3) 
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
        values.radar = c("0", "0.5", "1"), 
        plot.title = "By Category") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_shenzhen_all_by_category.jpg")

# Canada and All 

mydata_country <- mydata %>%
  filter((group == "Canada") | (group == "Average")) %>%
  mutate(P = rowMeans(.[,2:4])) %>%
  mutate(E = rowMeans(.[,5:7])) %>%
  mutate(R = rowMeans(.[,8:10])) %>%
  mutate(D = rowMeans(.[,11:13])) %>%
  select(c(group, P, E, R, D))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), 
         plot.title = "By Criterion") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_canada_all_by_criterion.jpg")

mydata_country <- mydata %>%
  filter((group == "Canada") | (group == "Average"))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
        values.radar = c("0", "0.5", "1"), 
        plot.title = "By Category") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_canada_all_by_category.jpg")

# Germany and All

mydata_country <- mydata %>%
  filter((group == "Germany") | (group == "Average")) %>%
  mutate(P = rowMeans(.[,2:4])) %>%
  mutate(E = rowMeans(.[,5:7])) %>%
  mutate(R = rowMeans(.[,8:10])) %>%
  mutate(D = rowMeans(.[,11:13])) %>%
  select(c(group, P, E, R, D))
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
         values.radar = c("0", "0.5", "1"), 
         plot.title = "By Criterion") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_germany_all_by_criterion.jpg")

mydata_country <- mydata %>%
  filter((group == "Germany") | (group == "Average")) 
ggradar(mydata_country, axis.label.size = 4, grid.label.size = 4, 
        values.radar = c("0", "0.5", "1"), 
        plot.title = "By Category") +
  theme(legend.position = "none") +
  ggsave(filename = "graphs/bli_germany_all_by_category.jpg")
```

## T Tests (BLI and Macroeconomic Indicators)

```{r}
t.test(mydata$gdp_growth[mydata$bli_category=="Low"], mydata$gdp_growth[mydata$bli_category=="High"])
t.test(mydata$gfcf[mydata$bli_category=="Low"], mydata$gfcf[mydata$bli_category=="High"])
t.test(mydata$recovery_rate[mydata$bli_category=="Low"], mydata$recovery_rate[mydata$bli_category=="High"])
t.test(mydata$cost[mydata$bli_category=="Low"], mydata$cost[mydata$bli_category=="High"])
t.test(mydata$time[mydata$bli_category=="Low"], mydata$time[mydata$bli_category=="High"])
```

#################

## Shenzhen Comparison (?)

```{r}
ggplot(mydata, aes(x = bli)) +
  geom_bar(stat = "identity") +
  geom_text(size = 4, aes(label = bli, hjust = 0.5, vjust = 3)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "BLI Scores Around the World",
    x = "Jurisdiction",
    y = "BLI Score",
    fill = "Continent") +
  ggsave(filename = "graphs/shenzhen_histograms.jpg")
```

## Regressions

```{r}
mydata_r <- lm(data = mydata, formula = gii ~ bli + gdp_growth + gfcf)
summary(mydata_r)
```

## Ariana -- Bloggers

```{r}
# Name of the file you want to read into the program in quotes. 
mydata <- read_csv(file = "graphs/ariana.csv")

# Change the words in quotes to filter for rows that contain different words.  
mydata_blog <- mydata %>% 
  filter(q5 %like% c("blog", "Blog"))

# Create a graph! You can change the title and axes labels as you wish. 
ggplot(mydata_blog, aes(x = q6)) +
  geom_bar() + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Level of Satisfaction",
    y = "Count",
    title = "Blogger Satisfaction"
  ) +
  ggsave(filename = "graphs/ariana_bloggers.jpg")

mydata_nonblog <- mydata %>% 
  filter(!q5 %like% c("blog", "Blog"))

ggplot(mydata_nonblog, aes(x = q6)) +
  geom_bar() + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Level of Satisfaction",
    y = "Count",
    title = "Non-Blogger Satisfaction"
  ) +
  ggsave(filename = "graphs/ariana_nonbloggers.jpg")

mydata_blog$value <- as.numeric(ifelse(mydata_blog$q6 == "A. Fully satisfied", '1',
                     ifelse(mydata_blog$q6 == "B. Basic Satisfaction", '2',
                     ifelse(mydata_blog$q6 == "C. Insufficient coverage area", '3',
                     ifelse(mydata_blog$q6 == "D. Too little visible area", '4', '5')))))

mydata_nonblog$value <- as.numeric(ifelse(mydata_nonblog$q6 == "A. Fully satisfied", '1',
                     ifelse(mydata_blog$q6 == "B. Basic Satisfaction", '2',
                     ifelse(mydata_blog$q6 == "C. Insufficient coverage area", '3',
                     ifelse(mydata_blog$q6 == "D. Too little visible area", '4', '5')))))

t.test(mydata_blog$value, mydata_nonblog$value)
```

## Ariana -- Students

```{r}
mydata <- read_csv(file = "graphs/ariana.csv")

mydata_blog <- mydata %>% 
  filter(q5 %like% c("student", "Student"))

ggplot(mydata_blog, aes(x = q6)) +
  geom_bar() + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Level of Satisfaction",
    y = "Count",
    title = "Student Satisfaction"
  ) +
  ggsave(filename = "graphs/ariana_students.jpg")

mydata_nonblog <- mydata %>% 
  filter(!q5 %like% c("student", "Student"))

ggplot(mydata_nonblog, aes(x = q6)) +
  geom_bar() + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Level of Satisfaction",
    y = "Count",
    title = "Non-Student Satisfaction"
  ) +
  ggsave(filename = "graphs/ariana_nonstudents.jpg")
```

```{r print-code, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```